On the Dynamics of Anthropomorphism in Robotics

### 2013-05-23 anthropomorphism.tex
Switch to Journal of Human-Robot Interaction template
You may need to install texlive-bibtex-extra to get the APA bibliography style

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

@@

\usepackage[draft]{fixme}

\journalname{Int J Soc Robot}

@@

\begin{document}

\title{On the Dynamics of Anthropomorphism in Robotics
\thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}
}
\subtitle{}

%\titlerunning{Short form of title}        % if too long for running head

\author{Julia Fink         \and
        S\'{e}verin Lemaignan     \and
        Pierre Dillenbourg  %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{J. Fink \and S. Lemaignan \and P. Dillenbourg \at
              Computer-Human Interaction in Learning and Instruction (CHILI) \\
              Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\
              Rolex Learning Center, Station 20 \\
              CH-1015 Lausanne \\
              Switzerland \\
              Tel.: +41-21-693-2274\\
              Fax: +41-21-693-6070\\
              \email{julia.fink@epfl.ch}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Lemaignan \at
              \email{severin.lemaignan@epfl.ch}
		   \and
           P. Dillenbourg \at
              \email{pierre.dillenbourg@epfl.ch}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}

	While anthropomorphism in robotics is a commonly discussed trait of human-robot interaction (HRI), it is paradoxically an overlooked research topic. This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{attributing human characteristics to robots}. It draws on social sciences and psychology, as well as on a critical survey of existing literature in the HRI community, to ground the concept of \textit{anthropomorphism}. We further present different kinds of \textit{anthropomorphic design} of robots and outline their role in social robotics. We then propose to go beyond the traditional perception of anthropomorphism as a static feature. We suggest to understand anthropomorphism as a dynamic, context-dependent process. This also provides an account of the so-called \textit{novelty effect}. To this end, we introduce an initial function of anthropomorphism that models the phenomenon along three interaction phases. Our function is supported by results of a long-term study that we conducted in a real human environment.

%	This article synthesizes the social phenomenon of attributing human characteristics to robots, and illustrates the role of human-like form and human social behavior cues in the design of robots. We draw on backgrounds from social sciences and psychology to first provide a common ground for the understanding of  anthropomorphism. The theoretical background is featured by an overview of different kinds of anthropomorphic design in robots. We also provide a comprehensive summary and critical comparison of findings from experiments studying anthropomorphism in human-robot interaction. Finally, we propose to understand anthropomorphism as a dynamic phenomenon which is not only determined by 1) \textit{individual characteristics} of the human user, and 2) the \textit{anthropomorphic design of the robot}, but might also be impacted by 3) \textit{dynamics}, such as \textit{time} and the \textit{context of use}. Consequently, we propose different levels of anthropomorphism that might shift with increased time of interaction and the context of use of a robot.

\keywords{
	Anthropomorphism \and
	Design \and    
    Human-Robot Interaction \and
    Social Issues in Robotics \and
    Acceptance of Robots}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

%\subsection{Subsection title}
%\label{sec:X.X}
%as required. Don't forget to give each section
%and subsection a unique label (see Sect.~\ref{sec:1}).
%\paragraph{Paragraph headings} Use paragraph headings as needed.
%\begin{equation}
%a^2+b^2=c^2
%\end{equation}

% For one-column wide figures use
% \begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{example.jpg}
% figure caption is below the figure
% \caption{Please write your figure caption here}
% \label{fig:1}       % Give a unique label
% \end{figure}
%
% For two-column wide figures use
% \begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
% \caption{Please write your figure caption here}
% \label{fig:2}       % Give a unique label
% \end{figure*}
%

\begin{acknowledgements}
AJung Moon, Aude Billard.\\
\end{acknowledgements}

% BibTeX users please use one of
 \bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{elsart-harv}
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{anthropomorphism}   % name your BibTeX data base

%\begin{thebibliography}{42}
%\providecommand{\natexlab}[1]{#1}
%\providecommand{\url}[1]{{#1}}
%\providecommand{\urlprefix}{URL }
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%\providecommand{\eprint}[2][]{\url{#2}}
%
%
%\bibitem[{Young et~al(2008)Young, Hawkins, Sharlin, and
%  Igarashi}]{young_toward_2008}
%Young JE, Hawkins R, Sharlin E, Igarashi T (2008) Toward acceptable domestic
%  robots: Applying insights from social psychology. International Journal of
%  Social Robotics 1(1):95--108
%
%
%\end{thebibliography}

% Non-BibTeX users please use
% \begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
% \bibitem{RefJ}
% Format for Journal Reference
% Author, Article title, Journal, Volume, page numbers (year)
% Format for books
% \bibitem{RefB}
% Author, Book title, page numbers. Publisher, place (year)
% etc
% \end{thebibliography}

%\paragraph{ }
%\begin{description}
$\newline$

\textbf{Julia Fink} is a PhD student in Human-Robot Interaction at EPFL. Her work focusses on the analysis of interaction, user experience and acceptance of robots in domestic spaces. She has a multi-disciplinary background in Media, Technology, Communication, and Interaction Studies. \\

\textbf{Dr. S\'{e}verin Lemaignan} is a postdoctoral researcher at EPFL. ...  \\

\textbf{Prof. Pierre Dillenbourg} is professor of learning technologies at EPFL. Former teacher in elementary school, he graduated in educational science (University of Mons, Belgium). He obtained a PhD in computer science from the University of Lancaster (UK), in the field of educational applications of artificial intelligence.  His work covers various domains of computer-supported collaborative learning (CSCL), ranging from novel interfaces for face-to-face collaboration (interactive furniture, tangibles, paper computing) to more cognitive projects on dual eye tracking.
%\end{description}

\end{document}
% end of file template.tex

>>>>

\documentclass[lettersize, apacite, twoside, HRI]{apa_HRI}
\usepackage{times} % Required package for HRI journal format

% UTF8 support
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

@@

\usepackage[draft]{fixme}
\rightheader{Journal of Human-Robot Interaction}
\leftheader{Fink et al.}

@@

\title{On the Dynamics of Anthropomorphism in Robotics
}

\author{Julia Fink, Séverin Lemaignan, Pierre Dillenbourg}
\affiliation{ Computer-Human Interaction in Learning and Instruction (CHILI) \\
              Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
              CH-1015 Lausanne, Switzerland
}
\abstract{While anthropomorphism in robotics is a commonly discussed trait of human-robot interaction (HRI), it is paradoxically an overlooked research topic. This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{attributing human characteristics to robots}. It draws on social sciences and psychology, as well as on a critical survey of existing literature in the HRI community, to ground the concept of \textit{anthropomorphism}. We further present different kinds of \textit{anthropomorphic design} of robots and outline their role in social robotics. We then propose to go beyond the traditional perception of anthropomorphism as a static feature. We suggest to understand anthropomorphism as a dynamic, context-dependent process. This also provides an account of the so-called \textit{novelty effect}. To this end, we introduce an initial function of anthropomorphism that models the phenomenon along three interaction phases. Our function is supported by results of a long-term study that we conducted in a real human environment.}

\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}

\begin{document}
\maketitle

@@

\section*{Acknowledgements}
AJung Moon, Aude Billard.\\

This research was supported by the Swiss National Science Foundation through
the National Centre of Competence in Research Robotics.

\section{Bibliography}
\bibliography{anthropomorphism}   % name your BibTeX data base

\hrule
\vspace*{.1in}
Authors' names and contact information: Julia Fink {\tt julia.fink@epfl.ch}, Séverin Lemaignan {\tt severin.lemaignan@epfl.ch}, Pierre Dillenbourg {\tt pierre.dillenbourg@epfl.ch}, CHILI Lab, EPFL, Lausanne, Switzerland.
\end{document}
